%!TEX root = sui14.tex
\vfill
%\ben{make sure no section title appears at the end of any column.}

\section{Background and Related Work}
Our approach is related to head- and eye-controlled interfaces, area cursors, pointing in physical spaces and computer vision-based selections.


\subsection{Head and Gaze Input}
Head movement has long been used for virtual camera control in VR applications~\cite{pausch_user_1993} and as an assistive input technology for cursor control of desktop applications~\cite{radwin1990method}. However, it is notable that human neck muscles have a lower bandwidth than other muscle groups, e.g., the wrist~\cite{card_morphological_1991}.
%
%Card, summarizing other work, shows that neck muscles are a poor muscle group for pointing in general: neck muscles only have a bandwidth of about $4.2bits/s$ (compared to $23bits/s$ of wrist muscles used by a standard mouse~\cite{Card:1991:MAD:123078.128726}.
%
Prior work often focused on head orientation for controlling graphical interfaces; in contrast, we apply this modality to selection in physical spaces.

Gaze can also be used to control graphical user interfaces~\cite{kumar2007eyepoint}. While there are wearable gaze trackers~\cite{bulling2009wearable}, turning information about a concrete point in space where a user is looking into a selection requires a map with known target locations.
Our system works through point-to-point IR communication and does not require an {\em a priori} map or markers. Target objects in the environment can also be equipped with individual cameras that watch the user~\cite{smith2013gaze,vertegaal2005media}. Such an approach can enable similar benefits as our approach, but is computationally more expensive and may not work at greater distances or angles, because it relies on finding the user's pupils in a camera image.

%Our work is closer in spirit to Selker's headworn system~\cite{Selker:2001:EGE:634067.634176}.

\subsection{Area Cursors}

In 2D area cursors for GUIs, the activation area of the cursor is enlarged, which facilitates acquiring smaller targets~\cite{kabbash1995prince}. We argue that head orientation pointing has analogous characteristics (limited pointing performance and accuracy). Area cursors are especially appropriate for individuals with motor control impairments or difficulties~\cite{worden1997making,findlater2010enhanced}. Similar ideas have also been extended into 3D to provide selection with progressive refinement in 3D scenes~\cite{bacim2013design}. All area and space cursors necessitate disambiguation when there are multiple targets and no clear winner. This paper describes the trade-offs between several disambiguation approaches.

%We conceptualize area pointing as a two-stage process: in the {\em coarse} phase, which we call {\em scanning}, users move so the activation area intersects with the target object (and possibly other, unintended targets). In the {\em refinement} phase, they adjust so only the intended target will be selected. Many disambiguation techniques are possible for refinement -- this paper describes the trade-offs between several of them.


\subsection{Pointing in Physical Spaces}
Rukzio \changes{et al.} ~\cite{rukzio_experimental_2006} studied alternative
methods for selecting devices in physical spaces and found that users strongly
preferred either tapping target appliances with a mobile device or pointing at a
distance to browsing a list. Several other approaches to spatial selection with
handheld
devices~\cite{beigl_point_1999,patel_2-way_2003,wilson_xwand:_2003,schmidt_picontrol:_2012,kemp_point-and-click_2008}
or finger-worn devices~\cite{merrill_augmenting_2007} exist.
%and exchanging information with smart infrastructure sensor networks ~\cite{lifton_tricorder:_2007,mittal_ubicorder:_2011,costanza_sensortune:_2010}.

In some techniques, users select objects of interest with laser pointers;
however, the laser dot's small target area makes it poorly matched to head
orientation input.  Other approaches rely on virtual room models in which a
user's location is estimated using IMU-based orientation
sensing~\cite{wilson_xwand:_2003,lifton_tricorder:_2007} -- in contrast, our
technique does not require a static map ahead of time. \changes{The FreeMote
system in \cite{hipp2009universal} is based on Wii platform and targeted at a
universal device access controller.  It's quite similar to our demonstrative
application, but could only work in rooms where only a few smart appliances
exist.}
% Other targeting systems use IR with handheld
% pointers~\cite{swindells_that_2002} as well as wearable devices such as rings
% and Bluetooth audio earpieces~\cite{merrill_augmenting_2007} to connect to
% smart devices.
Our system tackles an unresolved issue of prior approaches -- navigating an area
dense with potential targets and resolving selection ambiguity.

\subsection{Vision- and Projection-Based Target Selection}
Many alternative solutions for detecting devices in contained spaces
rely on computer-vision recognition of printed tags on devices. Unfortunately,
these methods either impose significant constraints on the camera used for
detection~\cite{Bokode}, require large or obtrusive tags~\cite{Dataglyphs}, or
are designed to work specifically at short distances~\cite{CyberCode}. Passive
markers also cannot show visual feedback in the environment.  Handheld
projectors can both display a user interface in space and communicate control
information optically, e.g., by encoding information temporally (using Gray
codes in Picontrol~\cite{schmidt_picontrol:_2012} and RFIG
Lamps~\cite{raskar_rfig_2004}) or spatially (using QR codes in the infrared
spectrum in SideBySide~\cite{willis_sidebyside:_2011}). Our solution is similar
in spirit but requires only small, low-cost IR emitters and detectors.


%However, visible tags at appropriate sizes may be rejected by users because of their negative aesthetic effect on the space.

%\subsection{Markers and Vision Methods}
%\achal{Not sure where to put this, feel free to move.}
%
%\ben{For CV, I think related work is one option to go; however, the requirement of being related work is that -- we need to reference them. There are a few examples ``require large, obtrusive tags, and inevitably lack feedback from passive devices in the environment'' which should be referenced. That's why I am thinking of putting this to discussion.}
%


%\ben{Reviewers suggest considering computer vision-based techniques with markers in the environment (such as %QR codes, or Bokode [Mohan] which extends the working distance to a few meters for visual tags). We considered this direction and found several drawbacks, including computational complexity, low accuracy when targets are far, the absence of real-time environment feedback with passive tags, and aesthetic issues with QR codes. While we don't claim our choice of IR is optimal, it has important advantages -- it is low-cost, readily available and quite suitable for area selection. We can weaken our claim and add explanations of how disambiguation techniques might generalize to other methods of implementing target identification.}

%\achal{Read and discussed the Bokode paper and CV in general. Unsure about what
%to do regarding "weakening our claim."}


%\ben{new related works from reviewers}. \bjoern{folded in}
%\changes{RFIG Lamps and photosensing wireless tags [Raskar et al] use a projector and data is encoded in each pixel so that tags can localize themselves for target selection. Our IR emitter, a relatively low-cost solution, doesn’t have this feature but shares the commonality of covering an area for the ease of selection. At the end of their paper, they envision an IR-based system to solve ambient light problems. Our work lies in that direction and also contributes evaluations with user studies.
%Progressive Refinement [Bacima] studies several progressive refinement selection modalities, which is close to our two-stage selection; but our contexts are head-orientation as it reflects users' point of interest.
%}
